---
title: "Relative and Absolute Pitch Data"
output_dir: docs
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
editor_options: 
  chunk_output_type: console
---

This dashboard is the current repository for the Relative and Absolute Pitch project between Eastman, Peabody, and the University of Amsterdam.

For questions, please contact [Dave Baker](mailto:davidjohnbaker1@gmail.com).

The current ordering reflects the questions as they are asked on the survey.

The total survey comprises $N = 73$ responses, when conditioned on location, some data only represent a single individual for an entire region or state. 

```{r}
#----------------------------------------------------------------------
library(dplyr)
library(magrittr)
library(readr)
library(ggplot2)
library(ggridges)
library(stringr)
library(usmap)
library(tidyr)
library(viridis)
#----------------------------------------------------------------------
source("R/cleaning_functions.R")
source("R/assemble_functions.R")
source("R/create_tables.R")
#----------------------------------------------------------------------


# Import Data For Analysis 

activity_table <- read_csv("data/cleaned_tables/activity_table.csv")
text_response_table <- read_csv("data/cleaned_tables/text_response_table.csv")
demographic_table <- read_csv("data/cleaned_tables/demographic_table.csv")
demo_key <- read_csv("data/demokey.csv")
states <- read.csv("data/temp_states - Sheet1.csv") %>% mutate(run_id = as.character(run_id))

# Remove Participants 

participants_to_exclude <- c(15)

'%!in%' <- function(x,y)!('%in%'(x,y))


activity_table <- activity_table %>%
  filter(run_id %!in% participants_to_exclude)

text_response_table <- text_response_table %>%
  filter(run_id %!in% participants_to_exclude)

demographic_table <- demographic_table %>%
  filter(run_id %!in% participants_to_exclude)

df <- df %>%
  filter(run_id %!in% participants_to_exclude)

def_table <- create_definition_table(df)

n_total_respondents <- demographic_table %>%
  select(run_id) %>%
  mutate(run_id = as.character(run_id)) %>%
  distinct() %>%
  nrow()

demo_key <- demo_key %>%
  rename(t_id = Key)

def_table_2 <- def_table %>%
  left_join(demo_key)

state_list <- df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 51) %>%
  mutate(response = str_remove_all(response, '[[:punct:]]')) %>%
  mutate(response = str_remove_all(response, "Q0")) 

# write.csv(state_list, "data/state_list.csv")

solfa_learned_table <- df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 50) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\"\\]\\}$")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\\"")) %>%
  separate(col = response, into = c("r1","r2","r3","r4","r5","r6","r7"),  sep = ",") %>%
  select(-trial_index) %>%
  pivot_longer(cols = r1:r7, names_to = "system",values_to = "response") %>%
  filter(!is.na(response))

solf_systems <- df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 50) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\"\\]\\}$")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\\"")) %>%
  separate(col = response, into = c("r1","r2","r3","r4","r5","r6","r7"),  sep = ",") %>%
  select(-trial_index) %>%
  pivot_longer(cols = r1:r7, names_to = "system",values_to = "response") %>%
  filter(!is.na(response)) %>%
  select(response) %>%
  distinct() 

solf_systems$solfa_group <- c("Moveable","Moveable","Moveable","Fixed",
                              "Moveable","Moveable","Moveable","Fixed","No Response","Moveable")


usa_map_solfa <- solfa_learned_table %>%
  left_join(states) %>%
  left_join(solf_systems) %>%
  filter(countr ==  "USA") %>%
  select(solfa_group, state) %>%
  group_by(state) %>%
  count(solfa_group)

usa_map_solfa[usa_map_solfa$solfa_group == "No Response",] <- NA

total_n_survey <- demographic_table %>%
  pull(run_id) %>%
  unique() %>%
  length()


```

### Abstract 

What does it mean for an individual to possess relative pitch (RP)? Do aural skills instructors agree on a single definition? How do they teach and assess RP in the classroom? Unlike absolute pitch (AP), which is the ability to produce or label a musical pitch without reference to an external standard (Marvin 2017), RP has no clearly agreed upon definition in the music-cognition and theory pedagogy literature: working definitions seem to capture some but not all aspects of this ability (Karpinski, 2000; Leipold et al., 2019; Levitin & Rogers, 2005; Marvin, 2007). Further while scholars have studied the prevalence (Ward, 1999 ), psychometric testing (Bermudez & Zatorre, 2009)), and neurophysiological mechanisms (Brauchli et al., 2019) of AP, RP has yet to receive such research attention.

Our research goal is twofold. The first is to disentangle beliefs about RP and AP in order to arrive at an empirical, inductive understanding of pitch-based skills. The second is to study the demographic, professional, and pedagogical factors that are associated with pedagogies of relative and absolute pitch. In order to accomplish this, we share data from a survey that asks music teachers (N = 42, ongoing) for definitions of RP and AP (e.g., Figure 1), classroom activities that foster them (e.g., Figure 2), and pedagogical beliefs about each (e.g., Figure 3). The survey also attempts to learn whether these attitudes are shaped by participants’ musical background and/or past teaching experiences (e.g., Figure 4). Data collection began in December 2021; complete findings will be shared at the conference. The poster will illustrate agreement plots and other graphical representations of the data (Figure 5). This research is part of a larger project to build a skills-test battery that captures absolute- and relative-pitch abilities; this battery will have implications for both music-cognitive research and classroom applications. 


### Definitions of Absolute and Relative Pitch 


```{r, fig.width=10, fig.height=7}

agreement_plot <- def_table_2 %>%
  filter(response != 8) %>%
  filter(Question != is.na(Question)) %>%
  mutate(APRP = case_when(
    APRP == "ap" ~ "Absolute Pitch",
    APRP == "rp" ~ "Relative Pitch",
  )) %>%
  ggplot(aes(y = reorder(Question, response), x = response, fill = APRP)) +
  geom_density_ridges2() +
  scale_x_continuous(limits = c(0,7), breaks = seq(1,7,1)) +
  labs(title = "Agreeing on Definitions of \nAbsolute and Relative Pitch",
       subtitle = paste("N = ", n_total_respondents),
       y = "Question",
       x = "Density",
       fill = "Question Bank") +
  theme_bw() +
  viridis::scale_fill_viridis(discrete = TRUE, begin = .1, end = .8)

agreement_plot
   
```

*** 

**Question**

Below are several possible definitions of relative pitch and absolute pitch. Using the seven point scale below, please indicate the degree to which you agree with each definition. The left hand side will always correspond with “I strongly disagree” and the right hand scale will correspond with “I strongly agree.” Selecting the middle of the scale would indicate that you neither agree nor disagree with the definition.

Remember that we are interested in what you think, based on your expertise and teaching experiences. We encourage you to use the full range of the rating scale.

Selecting NR (No Response) would indicate that you do not wish to respond to this question.

If none of these definitions matches your own personal definitions, you will have the chance to provide your own on the next page.

**Comments**

The first main plot here plots the general agreement and disagreement with each of the definitions of absolute and relative pitch.
Answers of "No Response" have been removed.

The answers are ordered in terms of the average response per question.
Answers at the top and bottom show the most grouping.

Eventually, the plan for this analysis is to PCA/Factor Analyse this data in order to see if both the AP/RP factors emerge as a dimension as well as the verbs.


### Relative Pitch Is... {data-commentary-width=400}

```{r}
df %>% 
  filter(trial_index == 3) %>%
  select(run_id, response ) %>%
  mutate(response = str_remove_all(response, '[[:punct:]]')) %>%
  mutate(response = str_remove_all(response, "Q0")) %>%
  filter(response != "NA") %>%
  filter(response != "not*.$") %>%
  filter(response != "na") %>%
  filter(response != "Not Applicable") %>%
  filter(response != "not applicable") %>%
  knitr::kable()

```

*** 

If you felt that none of the definitions of relative pitch on the page before were sufficient, please provide your own definition in the space below.

You are required to fill in some text. If you were happy with the definitions before, please just write Not Applicable.

Relative pitch is...


### Absolute Pitch is... 

```{r}
df %>% 
  filter(trial_index == 4) %>%
  select(run_id, response ) %>%
  mutate(response = str_remove_all(response, '[[:punct:]]')) %>%
  mutate(response = str_remove_all(response, "Q0")) %>%
  filter(response != "NA") %>%
  filter(response != "not*.$") %>%
  filter(response != "na") %>%
  filter(response != "Not Applicable") %>%
  filter(response != "not applicable") %>%
  knitr::kable()
```

*** 

If you felt that none of the definitions of absolute pitch were sufficient, please provide your own definition in the space below.

You are required to fill in some text. If you were happy with the definitions before, please just write Not Applicable.

Absolute pitch is...

### People With Absolute Pitch 

```{r, fig.width=10, fig.height= 7 }

people_table <- create_people_table(df)
people_key <- read_csv("PeopleTable2.csv")

people_key <- people_key %>%
  rename(t_id = key) %>%
  mutate(t_id = str_remove_all(t_id, "\'"))

people_plot <- people_table %>%
  left_join(people_key, by = "t_id") %>%
  filter(response != 8) %>%
  filter(Question != is.na(Question)) %>%
  mutate(APRP = case_when(
    APRP == "ap" ~ "Absolute Pitch",
    APRP == "rp" ~ "Relative Pitch"
  )) %>%
  ggplot(aes(y = reorder(Question, response), x = response, fill = APRP)) +
  geom_density_ridges2() +
  scale_x_continuous(limits = c(0,7), breaks = seq(1,7,1)) +
  labs(title = "Agreeing on Definitions of People\n with Absolute and Relative Pitch",
       subtitle = "N = 42",
       y = "Question",
       x = "Density",
       fill = "Question Bank") +
  theme_bw() +
  viridis::scale_fill_viridis(discrete = TRUE, begin = .1, end = .8)

people_plot

   

```

*** 

**Question**

Below are statements about people with relative and absolute pitch. Using the scale, please indicate the degree to which you agree with each statement, where the left hand side of the scale corresponds to 'I strongly disagree' and the right hand side of the scale corresponds to 'I strongly agree.' A selection in the middle would indicate that you neither agree nor disagree with the statement. Remember that we are interested in what you think, based on your expertise and teaching experiences.

**Comments**

### Select the average percentage of time per class period you currently spend fostering relative + absolute pitch skills.

```{r}
aprp_time_est_plot <- activity_table %>%
  filter(t_id %in% c("perc_class_time_ap", "perc_class_time_rp")) %>%
  mutate(response = as.numeric(response)) %>%
  mutate(t_id = case_when(
    t_id == "perc_class_time_ap" ~ "Absolute Pitch",
    t_id == "perc_class_time_rp" ~ "Relative Pitch"
  )) %>%
  ggplot(aes(response, fill = t_id)) +
  geom_histogram(bins = 40) +
  facet_wrap(~t_id, nrow = 2) +
  theme_bw() +
  viridis::scale_fill_viridis(discrete = TRUE, begin = .1, end = .8) +
  labs(title = "Classroom Time Devoted to \nAbsolute Pitch vs Relative Pitch in the Classroom",
       x = "Estimated Percentage of Time",
       y = "Frequency Count in Survey",
       fill = "Question Bank")

aprp_time_est_plot

```

*** 

**Notes**

This is presented as two questions, merged for one panel for analysis. 

AP RP in Classroom 

### How high a priority does your instituation/you put on relative/absolute pitch?

```{r}
activity_table %>%
  mutate(priority_bool = str_detect(t_id, "priority")) %>%
  filter(priority_bool == TRUE) %>%
  separate(col = t_id, into = c("who","priority","aprp","num"),sep = "_") %>%
  mutate(who = case_when(
    who == "inst" ~ "Institution",
    who == "you" ~ "You"
  )) %>%
  mutate(APRP = case_when(
    aprp == "ap" ~ "Absolute Pitch",
    aprp == "rp" ~ "Relative Pitch"
  )) %>%
  mutate(q_id = paste(who,"prioritises", APRP,"?")) %>%
  mutate(response = as.numeric(response)) %>%
  ggplot(aes(x = response)) +
  geom_histogram() +
  facet_wrap(~q_id) +
  theme_bw() + 
  labs(title = "Who prioriti[sz]es what?",
       x = "Low Priority             <<                                                                 >>          High Priority")
  
```

*** 

- How high a priority does your institution's curriculum place in developing absolute pitch in your students?
- How high a priority does your institution's curriculum place in developing relative pitch in your students?
- How high a priority do you place in developing absolute pitch in your students?
- How high a priority do you place in developing relative pitch in your students?

**Notes**


### Use the text box below to describe a classroom activity you either use, know of, or can imagine that could be used to foster relative pitch in the classroom.

```{r}

df %>% 
  filter(trial_index %in% c(12,14,16,18,20)) %>%
  select(run_id, response) %>%
  mutate(response = str_remove_all(response, '[[:punct:]]')) %>%
  mutate(response = str_remove_all(response, "Q0")) %>%
  knitr::kable()

```

*** 

**Question**

Use the text box below to describe a classroom activity you either use, know of, or can imagine that could be used to foster relative pitch in the classroom.

This is the first of five activities you will be prompted to give regarding relative pitch.

We require you to provide at least one activity using this page, and we will ask you to provide more activities on subsequent pages (although no response will be required for subsequent activities).

Please describe the activity below. The next slide will ask you to rate the which you described on several dimensions.

Your response will inform perceptual tasks we hope to build at a later stage of this research.

**Notes**

TODO: Join on Difficulty Level for Single Activities 
TODO: Check Import Code, some answers lost because csv import error!


### Use the text box below to describe a classroom activity you either use, know of, or can imagine that could be used to foster absolute pitch in the classroom.

```{r}
df %>% 
  filter(trial_index %in% c(25, 27, 29, 31, 33)) %>%
  select(run_id, response) %>%
  mutate(response = str_remove_all(response, '[[:punct:]]')) %>%
  mutate(response = str_remove_all(response, "Q0")) %>%
  knitr::kable()
```

*** 

**Question**

Use the text box below to describe a classroom activity you either use, know of, or can imagine that could be used to foster absolute pitch in the classroom.

This is the first of five activities you will be prompted to give regarding absolute pitch.

We require you to provide at least one activity using this page, and we will ask you to provide more activities on subsequent pages (although no response will be required for subsequent activities).

Please describe the activity below. The next slide will ask you to rate the activity which you described on several dimensions.

Your response will inform perceptual tasks we hope to build at a later stage of this research.

**Notes**

TODO Make same merged table as in RP parallel question. 

### Please list examples of repertoire you use in your aural skills teaching (folk songs, Bach chorales, jazz, etc.).


```{r}

text_response_table %>%
  filter(t_id == "rep_list_free_response") %>%
  select(run_id, response) %>%
  knitr::kable()

```

*** 

### What percentage of your overall aural skills teaching time do you spend on Western classical repertoire compared to all other musical styles?

```{r}
df %>%
  filter(trial_index == 34) %>%
  select(run_id, response) %>%
  mutate(response = as.numeric(response)) %>%
  ggplot(aes(x = response)) +
  geom_histogram() +
  theme_bw() +
  labs(title = "Percent of Time On Classical Rep")
   

state_rep <- df %>%
  filter(trial_index == 34) %>%
  select(run_id, response) %>%
  mutate(response = as.numeric(response)) %>%
  left_join(states) %>%
  filter(countr == "USA") %>%
  group_by(state) %>%
  summarise(mean_time = mean(response))


# La Based vs Do Based Minor 
plot_usmap(data = state_rep, values = "mean_time") + 
  scale_fill_continuous(name = "Population (2015)", label = scales::comma) + 
  theme(legend.position = "right") +
  labs(title = "What percentage of time do you spend on classical repertoire?")

```

*** 

**Question**

What percentage of your overall aural skills teaching time do you spend on Western classical repertoire compared to all other musical styles?

Putting the slider to the far left would indicate you spend 0% of the time on Western classical repertoire. Moving the slider to the far right would indicate you spend 100% of your time on Western classical repertoire.

**Notes**


### What repertoire do you wish you could teach or intend to teach in the aural skills classroom if given the opportunity?

```{r}
text_response_table %>%
  filter(t_id == "rep_list_intend_response") %>%
  select(run_id, response) %>%
  knitr::kable()
```

*** 

### Please list any activities you do in the aural skills classroom that don’t involve musical staff notation.

```{r}



text_response_table %>% 
  select(run_id, response) %>%
  knitr::kable()
```

*** 



### What percentage of your teaching time in the aural skills classroom do you spend on activities that don't depend on notation?


```{r}
no_notation_map <- df %>%
  filter(trial_index == 37) %>%
  select(run_id, response) %>%
  mutate(run_id = as.character(run_id)) %>%
  left_join(states) %>%
  filter(countr == "USA") %>%
  group_by(state) %>%
  mutate(response = as.numeric(response)) %>%
  summarise(mean_no_notation = mean(response))

plot_usmap(data = no_notation_map, values = "mean_no_notation") + 
  scale_fill_continuous(name = "Population (2015)", label = scales::comma) + 
  theme(legend.position = "right") +
  labs(title = "What percentage of your teaching time in the aural skills classroom do you spend on activities\n that don't depend on notation?")


df %>%
  filter(trial_index == 37) %>%
  select(run_id, response) %>%
  mutate(response = as.numeric(response)) %>%
  ggplot(aes(x = response)) +
  geom_histogram() +
  theme_bw() +
  labs(title = "Percent of Time Don't Depend on Notation") 

```

*** 



### What activities represent the majority of your teaching responsibilities? Choose all that apply.

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 40) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\]\\}$"))
  

# df %>%
#   select(run_id, trial_index, response) %>%
#   filter(trial_index == 40)  %>%
#   knitr::kable()
```

*** 

text

### How many years have you been teaching music in the classroom?


```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 41)  %>%
  mutate(response = str_remove_all(response, '[[:punct:]]')) %>%
  mutate(response = str_remove_all(response, "Q0")) %>%
  mutate(response = as.numeric(response)) %>%
  mutate(median_years = median(response, na.rm = TRUE)) %>%
  ggplot(aes(x = response)) +
  geom_histogram() +
  geom_vline(xintercept = 19) +
  labs(title = "How many years have you been teaching music in the classroom?",
       subtitle = "Median @ 19 Years") +
  theme_bw()
  
```

*** 

- Obvious 85 outlier for 85 years of teaching! 

### Please list the highest ranked degree you have earned.

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 42) %>%
    mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\"\\]\\}$")) %>%
  count(response) %>%
  ggplot(aes(x = reorder(response,n), y = n)) +
  geom_histogram(stat = "identity") +
  theme_bw() +
  coord_flip() +
  labs(title = "Please list the highest ranked degree you have earned.")
  

```

*** 

text

### About how many years has it been since graduating with your highest earned degree?

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 43) %>%
  mutate(response = str_remove_all(response, '[[:punct:]]')) %>%
  mutate(response = str_remove_all(response, "Q0")) %>%
  knitr::kable()
```

*** 

text


### From what type of institution was your most recent degree?

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 44) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\"\\]\\}$"))

```

*** 

text

### What teaching role best describes you? Please choose one.

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 45) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\}$")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\"$")) %>%
  count(response) %>%
  ggplot(aes(x = reorder(response,n), y = n)) +
  geom_histogram(stat = "identity") +
  theme_bw() +
  coord_flip() +
  labs(title = "What teaching role best describes you? Please choose one")
         
```

*** 

text

### I would characterize my own sense of absolute pitch as:

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 46) %>%
  mutate(response = as.numeric(response)) %>%
  ggplot(aes(x = response)) +
  geom_histogram() +
  labs(title = "I would characterize my own sense of absolute pitch as:") +
  theme_bw()
  
```

*** 

text

### I would characterize my own sense of relative pitch as:

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 47) %>%
  mutate(response = as.numeric(response)) %>%
  ggplot(aes(x = response)) +
  geom_histogram() +
  labs(title = "I would characterize my own sense of relative pitch as:") +
  theme_bw()
  
```

*** 

text

### How many years of aural skills have you taught in your professional career?

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 49) %>%
  mutate(response = str_remove_all(response, '[[:punct:]]')) %>%
  mutate(response = str_remove_all(response, "Q0")) %>%
  mutate(response = str_remove_all(response, "\ years")) %>%
  mutate(response = str_remove_all(response, "asdf")) %>%
  mutate(response = as.numeric(response)) %>%
  ggplot(aes(x = response)) +
  geom_histogram() +
  theme_bw() +
  labs(title = "How many years of aural skills have you taught in your professional career?")
  
  
  
```

*** 

text

### What system did you learn when you were a student? Select all that apply.

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 50) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\"\\]\\}$")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\\"")) %>%
  separate(col = response, into = c("r1","r2","r3","r4","r5","r6","r7"),  sep = ",") %>%
  select(-trial_index) %>%
  pivot_longer(cols = r1:r7, names_to = "system",values_to = "response") %>%
  filter(!is.na(response)) %>%
  knitr::kable()

  
# solf_systems$dola <- c("La","Letter","Do","Fixed","")



```

*** 

text

### Where were you when you learned this system as a student?

```{r}

df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 51) %>%
  mutate(response = str_remove_all(response, '[[:punct:]]')) %>%
  mutate(response = str_remove_all(response, "Q0")) %>%
  knitr::kable()

```

*** 

text

### USA Solfa Map 

```{r}


library(usmap)

usa_map_solfa %>% View()

# La Based vs Do Based Minor 
solfa_map_with_na <- plot_usmap(data = usa_map_solfa, values = "n") + 
  scale_fill_continuous(name = "Number of Responses Per State", label = scales::comma) + 
  theme(legend.position = "right") +
  facet_wrap(~solfa_group, nrow = 3, ncol = 1)


ggsave(filename = "img/fig/solfa_map_with_na.png", plot = solfa_map_with_na, dpi = 300, height = 8, width = 4)

```

*** 

text

### What system do you prefer to teach? Select all that apply.


```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 52) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\"\\]\\}$")) %>%
  knitr::kable()

```

*** 

text

### What system do you primarily teach at your institution? Select all that apply.

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 53) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\"\\]\\}$")) %>%
  knitr::kable()

```

*** 

text

### How many students are typically enrolled in one of your aural skills classes (or sections)?

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 54) %>%
  mutate(response = str_remove_all(response, '[[:punct:]]')) %>%
  mutate(response = str_remove_all(response, "Q0")) %>%
  knitr::kable()

```

*** 


### Tracking, Pitch Memory, Clefts 

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 55) %>%
  knitr::kable()
```

*** 

asdf


*** 

asdf

### In what type of institution do you teach? Choose all that apply.

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 56) %>%
  knitr::kable()
```

*** 

asdf

### Approximately how many music majors are enrolled in the music program where you've most recently taught?

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 57) %>%
  knitr::kable()
```

*** 

Approximately how many music majors are enrolled in the music program where you've most recently taught? Please include both undergraduate and graduate students if your school offers both. If you don't wish to provide a response, write 'No Response'.

### Please list the degrees/programs your current or most recent music program offers. Choose all that apply:

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 58) %>%
  knitr::kable()
```

*** 

asdf

### What rank do most aural skills teachers hold at your institution? Choose all that apply.

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 59) %>%
  knitr::kable()
```

*** 
asdf 

### What is the highest degree that MOST aural skills teachers have at your institution? Choose all that apply.


```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 60) %>%
  knitr::kable()
```

*** 

asdf

### In what country do you teach?

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 61) %>%
  mutate(response = str_remove_all(response, '[[:punct:]]')) %>%
  mutate(response = str_remove_all(response, "Q0")) %>%
  knitr::kable()

```

*** 
asdf

### In what state or province do you teach? Leave blank if not applicable.


```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 62) %>%
  mutate(response = str_remove_all(response, '[[:punct:]]')) %>%
  mutate(response = str_remove_all(response, "Q0")) %>%
  knitr::kable()
```

*** 

asdf


### Do you have any feedback you would like to provide on this survey?

```{r}
df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 63) %>%
  mutate(response = str_remove_all(response, '[[:punct:]]')) %>%
  mutate(response = str_remove_all(response, "Q0")) %>%
  knitr::kable()
```

*** 

asdf

### Alluvial Chart Ideas 

```{r}
library(ggalluvial)

# System Learned As Student 

system_learned <- df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 50) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\"\\]\\}$")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\\"")) %>%
  separate(col = response, into = c("r1","r2","r3","r4","r5","r6","r7"),  sep = ",") %>%
  select(-trial_index) %>%
  pivot_longer(cols = r1:r7, names_to = "system",values_to = "response") %>%
  filter(!is.na(response)) %>%
  mutate(timepoint = "student")


# Prefer to Teach
system_prefer <- df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 52) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\"\\]\\}$")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\\"")) %>%
  separate(col = response, into = c("r1","r2","r3","r4","r5","r6","r7"),  sep = ",") %>%
  select(-trial_index) %>%
  pivot_longer(cols = r1:r7, names_to = "system",values_to = "response") %>%
  filter(!is.na(response)) %>%
  mutate(timepoint = "prefer")


# Teach At Institution 
system_institution <- df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 53) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\"\\]\\}$")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\\"")) %>%
  separate(col = response, into = c("r1","r2","r3","r4","r5","r6","r7"),  sep = ",") %>%
  select(-trial_index) %>%
  pivot_longer(cols = r1:r7, names_to = "system",values_to = "response") %>%
  filter(!is.na(response)) %>%
  mutate(timepoint = "institution")


alluvial_data <- rbind(system_learned, system_prefer, system_institution)

# TODO: Add Histogram of WHO is taking this survey (as histogram or something )
# TODO: Do up colors

alluvial_chart <- alluvial_data %>%
  group_by(timepoint) %>%
  count(response) %>%
  mutate(timepoint = case_when(
    timepoint == "student" ~ "Learned As Student",
    timepoint == "prefer" ~ "System Prefer to Teach",
    timepoint == "institution" ~ "Currently Teach at Institution",
  )) %>%
  mutate(timepoint = factor(timepoint, levels = c("Learned As Student","System Prefer to Teach","Currently Teach at Institution"))) %>%
  ggplot(aes(x = timepoint, y = n, alluvium = response)) +
  geom_alluvium(aes(fill = response, color = response),
                alpha = .75, decreasing = FALSE) +
  theme_bw() +
  labs(title = "Alluvial Chart", x = "Time Point",
       y = "Number of Responses", 
       color = "System", fill = "System")


ggsave(filename = "img/fig/alluvial_chart.png",plot = alluvial_chart, dpi = 300, height = 9, width = 13)

```

*** 

Retrospectively should have done ranked categories. 


### Response Map 

```{r}
# Import Spreadsheet with States



```

*** 

asdf


### References 


Bermudez, P. & Zatorre, R. J. (2009). A distribution of absolute pitch ability as revealed by computerized testing. Music Perception, 27(2), 89–101.

Brauchli, C., Leipold, S.& Jäncke, L. (2019). Univariate and multivariate analyses of functional networks in absolute pitch. Neuroimage, 189, 241–247.

Burns, E. M., & Campbell, S. L. (1994). Frequency and frequency-ratio resolution by possessors of absolute and relative pitch: Examples of categorical perception? Journal of the Acoustical Society of America, 96(5, Pt 1), 2704–2719. https://doi.org/10.1121/1.411447

Deutsch, D. (2013). Absolute pitch. In The psychology of music (ed. D. Deutsch), 3rd ed., 141–182. Academic Press.

Deutsch, D., Henthorn, T., Marvin, E., & Xu, H. (2006). Absolute pitch among American and Chinese conservatory students: Prevalence differences and evidence for a speech-related critical period. Journal of the Acoustical Society of America, 119, 719–722.

Halpern, A. R. (1989). Memory for the absolute pitch of familiar songs. Memory & Cognition, 17, 572–581.

Karpinski, G. S. (2000). Aural skills acquisition: The development of listening, reading, and performing skills in college-level musicians. Oxford University Press.

Leipold, S., Brauchli, C., Greber, M., & Jäncke, L. (2019). Absolute and relative pitch processing in the human brain: Neural and behavioral evidence. Brain Structure and Function, 224, 1723–1738. doi:10.1007/s00429-019-01872-2 pmid:30968240

Leipold, S., Greber, M., & Elmer, S. (2019) Perception and cognition in absolute pitch: distinct yet inseparable. The Journal of Neuroscience, 39, 5839–5841. doi:10.1523/JNEUROSCI.0653-19.2019 pmid:31341067

Levitin, D. J. (1994). Absolute memory for musical pitch: Evidence from the production of learned memories. Perception & Psychophysics, 56, 414–423.

Levitin, D., & Rogers, S. (2005). Absolute pitch: Perception, coding, and controversies. Trends in Cognitive Sciences, 9(1), 26–33.

Marvin, E. W. (2007). Absolute pitch perception and the pedagogy of relative pitch. Journal of Music Theory Pedagogy, 21, 1–34.

Marvin, E. W. (2017). Musical connections: Absolute pitch. In The Routledge companion to music cognition (ed. Richard Ashley and Renée Timmers), 203–212. Routledge.

Marvin, E. W, VanderStel, J., & Siu, J. C. (2020). In their own words: Analyzing the extents and origins of absolute pitch. Psychology of Music, 48(6), 808–823. doi:10.1177/0305735619832959 

McClaskey, C. M. (2016). Factors affecting relative pitch perception. [Doctoral dissertation, University of California, Irvine].

Miyazaki, K., & Rakowski, A. (2002). Recognition of notated melodies by possessors and nonpossessors of absolute pitch. Perception & Psychophysics, 64, 1337–1345.

Rogers, M. R. (2004). Teaching approaches in music theory: An overview of pedagogical philosophies, 2nd ed. Southern Illinois University Press.

Plantinga, J., & Trainor, L. J. (2005). Memory for melody: Infants use a relative pitch code. Cognition, 98(1), 1–11.

Schellenberg, E. G., & Trehub, S. E. (2003). Good pitch memory is widespread. Psychological Science, 14, 262–266.

Van Hedger, S. C., Veillette, J., Heald, S. L. M., & Nusbaum, H. C. (2020). Revisiting discrete versus continuous models of human behavior: The case of absolute pitch. PLoS ONE, 15(12), Article e0244308. https://doi.org/10.1371/journal.pone.0244308

Ward, W. D. (1999). Absolute pitch. In The psychology of music (ed. D. Deutsch), 265–298. Academic Press.