---
title: "Pedagogy 2 Practice Markdown"
author: "David John Baker"
date: "4/21/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

This document contains code for the figures made for the Pedagogy to Practice 2022 poster for this project.

```{r}
#----------------------------------------------------------------------
library(dplyr)
library(magrittr)
library(readr)
library(ggplot2)
library(ggridges)
library(stringr)
library(usmap)
library(tidyr)
library(viridis)
#----------------------------------------------------------------------
source("R/cleaning_functions.R")
source("R/assemble_functions.R")
source("R/create_tables.R")
#----------------------------------------------------------------------
# Import Data For Analysis 

activity_table <- read_csv("data/cleaned_tables/activity_table.csv")
text_response_table <- read_csv("data/cleaned_tables/text_response_table.csv")
demographic_table <- read_csv("data/cleaned_tables/demographic_table.csv")
demo_key <- read_csv("data/demokey.csv")
states <- read.csv("data/temp_states - Sheet1.csv") %>% mutate(run_id = as.character(run_id))

#----------------------------------------------------------------------
# Temporary Functions  

'%!in%' <- function(x,y)!('%in%'(x,y))


#----------------------------------------------------------------------
# Remove Participants 

participants_to_exclude <- c(15)

#----------------------------------------------------------------------
# Temporary Functions  

activity_table <- activity_table %>%
  filter(run_id %!in% participants_to_exclude)

text_response_table <- text_response_table %>%
  filter(run_id %!in% participants_to_exclude)

demographic_table <- demographic_table %>%
  filter(run_id %!in% participants_to_exclude)

df <- df %>%
  filter(run_id %!in% participants_to_exclude)

def_table <- create_definition_table(df)

n_total_respondents <- demographic_table %>%
  select(run_id) %>%
  mutate(run_id = as.character(run_id)) %>%
  distinct() %>%
  nrow()

demo_key <- demo_key %>%
  rename(t_id = Key)

def_table_2 <- def_table %>%
  left_join(demo_key)

state_list <- df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 51) %>%
  mutate(response = str_remove_all(response, '[[:punct:]]')) %>%
  mutate(response = str_remove_all(response, "Q0")) 

# write.csv(state_list, "data/state_list.csv")

solfa_learned_table <- df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 50) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\"\\]\\}$")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\\"")) %>%
  separate(col = response, into = c("r1","r2","r3","r4","r5","r6","r7"),  sep = ",") %>%
  select(-trial_index) %>%
  pivot_longer(cols = r1:r7, names_to = "system",values_to = "response") %>%
  filter(!is.na(response))

solf_systems <- df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 50) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\"\\]\\}$")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\\"")) %>%
  separate(col = response, into = c("r1","r2","r3","r4","r5","r6","r7"),  sep = ",") %>%
  select(-trial_index) %>%
  pivot_longer(cols = r1:r7, names_to = "system",values_to = "response") %>%
  filter(!is.na(response)) %>%
  select(response) %>%
  distinct() 

solf_systems$solfa_group <- c("Moveable","Moveable","Moveable","Fixed",
                              "Moveable","Moveable","Moveable","Fixed","No Response","Moveable")


usa_map_solfa <- solfa_learned_table %>%
  left_join(states) %>%
  left_join(solf_systems) %>%
  filter(countr ==  "USA") %>%
  select(solfa_group, state) %>%
  group_by(state) %>%
  count(solfa_group)

usa_map_solfa[usa_map_solfa$solfa_group == "No Response",] <- NA

total_n_survey <- demographic_table %>%
  pull(run_id) %>%
  unique() %>%
  length()

```

## Column A

### Breakdown of Survey Respondents 

```{r}

where_teach <- df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 56)  %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\]\\}$")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = ",NASM-accredited music program")) %>%
  count(response) %>%
  ggplot(aes(x = reorder(response, n), y = n)) +
  geom_histogram(stat = "identity") +
  coord_flip() +
  theme( axis.text = element_text(size = 14 )) +
  labs(title = "Where do our respondents teach?",
       x = "Description of School",
       y = "Number of Responses")
  
where_teach

ggsave(filename = "img/fig/where_teach.png",where_teach, dpi = 300, height = 9, width = 12)

  
what_teach <- df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 40) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\]\\}$")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\\"")) %>%
  separate(col = response, into = c("r1","r2","r3","r4","r5","r6","r7","r8","r9","r10","r11","r12"),  sep = "\\),") %>%
  select(-trial_index) %>%
  pivot_longer(cols = r1:r12, names_to = "responsibility", values_to = "response") %>%
  mutate(response = str_remove_all(response, pattern = "[[:punct:]]")) %>%
  filter(!is.na(response)) %>%
  count(response) %>%
  ggplot(aes(x = reorder(response, n), y = n)) +
  geom_histogram(stat = "identity") +
  coord_flip() +
  theme( axis.text = element_text(size = 14 )) +
  labs(title = "Total Counts of Teaching Reponse Across Survey", 
       x = "Description of Teaching",
       y = "Number of Responses")

what_teach  

ggsave(filename = "img/fig/what_teach.png", what_teach, dpi = 300, height = 9, width = 12)


what_cow <- cowplot::plot_grid(where_teach, what_teach, ncol = 1)

ggsave(filename = "img/fig/what_cow.png", what_cow, dpi = 300, height = 15, width = 20)


```


### Breakdown of Classroom Time Devoted to RP and AP 

```{r}
aprp_time_est_plot <- activity_table %>%
  filter(t_id %in% c("perc_class_time_ap", "perc_class_time_rp")) %>%
  mutate(response = as.numeric(response)) %>%
  mutate(t_id = case_when(
    t_id == "perc_class_time_ap" ~ "Absolute Pitch",
    t_id == "perc_class_time_rp" ~ "Relative Pitch"
  )) %>%
  ggplot(aes(response, fill = t_id)) +
  geom_freqpoly(aes(color = t_id)) +
  facet_wrap(~t_id, nrow = 2) +
  theme_bw() +
  viridis::scale_color_viridis(discrete = TRUE, begin = .1, end = .8) +
  labs(title = "Classroom Time Devoted to \nAbsolute Pitch vs Relative Pitch in the Classroom",
       x = "Estimated Percentage of Time",
       y = "Frequency Count in Survey",
       color = "Question Bank")

aprp_time_est_plot

ggsave(filename = "img/fig/aprp_time_est_plot.png", aprp_time_est_plot, dpi = 300, height = 6, width = 12)

```



### Alluvial Chart 

```{r}
library(ggalluvial)

# System Learned As Student 

system_learned <- df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 50) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\"\\]\\}$")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\\"")) %>%
  separate(col = response, into = c("r1","r2","r3","r4","r5","r6","r7"),  sep = ",") %>%
  select(-trial_index) %>%
  pivot_longer(cols = r1:r7, names_to = "system",values_to = "response") %>%
  filter(!is.na(response)) %>%
  mutate(timepoint = "student")


# Prefer to Teach
system_prefer <- df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 52) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\"\\]\\}$")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\\"")) %>%
  separate(col = response, into = c("r1","r2","r3","r4","r5","r6","r7"),  sep = ",") %>%
  select(-trial_index) %>%
  pivot_longer(cols = r1:r7, names_to = "system",values_to = "response") %>%
  filter(!is.na(response)) %>%
  mutate(timepoint = "prefer")


# Teach At Institution 
system_institution <- df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 53) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\\[\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\"\\]\\}$")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\\"")) %>%
  separate(col = response, into = c("r1","r2","r3","r4","r5","r6","r7"),  sep = ",") %>%
  select(-trial_index) %>%
  pivot_longer(cols = r1:r7, names_to = "system",values_to = "response") %>%
  filter(!is.na(response)) %>%
  mutate(timepoint = "institution")


alluvial_data <- rbind(system_learned, system_prefer, system_institution)

# TODO: Add Histogram of WHO is taking this survey (as histogram or something )
# TODO: Do up colors

alluvial_chart <- alluvial_data %>%
  group_by(timepoint) %>%
  count(response) %>%
  left_join(solf_systems) %>%
  mutate(timepoint = case_when(
    timepoint == "student" ~ "Learned As Student",
    timepoint == "prefer" ~ "System Prefer to Teach",
    timepoint == "institution" ~ "Currently Teach at Institution",
  )) %>%
  mutate(timepoint = factor(timepoint, levels = c("Learned As Student","System Prefer to Teach","Currently Teach at Institution"))) %>%
  ggplot(aes(x = timepoint, y = n, alluvium = response)) +
  geom_alluvium(aes(fill = response, color = response),
                alpha = .75, decreasing = FALSE) +
  theme_bw() +
  viridis::scale_fill_viridis(discrete = TRUE,option = "B") +
  viridis::scale_color_viridis(discrete = TRUE,option = "B") +
  labs( x = "Time Point",
       y = "Number of Responses", 
       color = "System", fill = "System")

alluvial_chart

ggsave(filename = "img/fig/alluvial_chart.png",plot = alluvial_chart, dpi = 300, height = 9, width = 14)

```


### Years Teaching In Classroom 

```{r}
teaching_rank <- df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 45) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\{\"Colors\"\\:\"")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\\}$")) %>%
  mutate(response = str_remove_all(string = response,pattern = "\"$")) %>%
  select(run_id, response) %>%
  rename(type_role = response)


years_teaching <- df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 41)  %>%
  mutate(response = str_remove_all(response, '[[:punct:]]')) %>%
  mutate(response = str_remove_all(response, "Q0")) %>%
  mutate(response = as.numeric(response)) %>%
  mutate(median_years = median(response, na.rm = TRUE)) %>%
  filter(response < 75) %>%
  left_join(teaching_rank) %>%
  ggplot(aes(x = response, fill = type_role)) +
  geom_dotplot(binwidth = 2, alpha = .8) +
  labs(title = "How many years have you been teaching music in the classroom?",
       x = "Number of Years", fill = "Type of Role") +
  theme_bw() +
  viridis::scale_fill_viridis(discrete = TRUE,option = "C") +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

ggsave(filename = "img/fig/years_teaching.png",plot = years_teaching, dpi = 300, height = 3, width = 10)

years_teaching  
```


### Map of Sofla

```{r}
# La Based vs Do Based Minor 
solfa_map_with_na <- plot_usmap(data = usa_map_solfa, values = "n") + 
  scale_fill_continuous(name = "Number of Responses Per State", label = scales::comma) + 
  theme(legend.position = "right") +
  facet_wrap(~solfa_group, nrow = 1, ncol = 4) +
  scale_fill_viridis() +
    theme() +
  labs(title = "Location of Domestic Responses: Fixed Versus Moveable Do",
       fill = "Count")

solfa_map_with_na

ggsave(filename = "img/fig/solfa_map_with_na.png", plot = solfa_map_with_na, dpi = 300, height = 3, width = 6)


df %>%
  select(run_id, trial_index, response) %>%
  filter(trial_index == 61) %>%
  mutate(response = str_remove_all(response, '[[:punct:]]')) %>%
  mutate(response = str_remove_all(response, "Q0")) %>%
  count(response)

11 + 1 + 5 + 1 + 35 + 1

manual_country <- tibble(country = c("China","Canada","Does Not Teach","Malta","USA","UK"),
                         n = c(14,1,1,1,54, 1))

country_plot <- manual_country %>%
  ggplot(aes(x = country,y = n, fill = country)) +
  geom_bar(stat = "identity") +
  labs(title = "Location ",
       x =  "Country",
       y = "Frequency",
       fill = "Country") +
  scale_fill_viridis(option = "A", discrete = TRUE) +
  theme_bw()


ggsave(filename = "img/fig/country_plot.png", plot = country_plot, dpi = 300, height = 4, width = 8)
```





## Column B 

### Definitions of AP and RP 


```{r}
agreement_plot <- def_table_2 %>%
  filter(response != 8) %>%
  filter(Question != is.na(Question)) %>%
  mutate(APRP = case_when(
    APRP == "ap" ~ "Absolute Pitch",
    APRP == "rp" ~ "Relative Pitch",
  )) %>%
  ggplot(aes(y = reorder(Question, response), x = response, fill = APRP)) +
  geom_density_ridges2(panel_scaling = FALSE, scale = 3) +
  scale_x_continuous(limits = c(0,7), breaks = seq(1,7,1)) +
  labs(title = "Agreeing on Definitions of \nAbsolute and Relative Pitch",
       subtitle = paste("N = ", n_total_respondents),
       y = "Question",
       x = "  Strongly Disagree     Strongly Agree",
       fill = "Question Bank") +
  theme_bw() +
  viridis::scale_fill_viridis(discrete = TRUE, begin = .1, end = .8, alpha = .75)

agreement_plot

ggsave(filename = "img/fig/p2p_agreementplot.png", agreement_plot, dpi = 300, height = 9, width = 9)

```


### Definitions of People with AP and RP 


```{r}
people_table <- create_people_table(df)
people_key <- read_csv("PeopleTable2.csv")

people_key <- people_key %>%
  rename(t_id = key) %>%
  mutate(t_id = str_remove_all(t_id, "\'"))

people_plot <- people_table %>%
  left_join(people_key, by = "t_id") %>%
  filter(response != 8) %>%
  filter(Question != is.na(Question)) %>%
  mutate(APRP = case_when(
    APRP == "ap" ~ "Absolute Pitch",
    APRP == "rp" ~ "Relative Pitch"
  )) %>%
  ggplot(aes(y = reorder(Question, response), x = response, fill = APRP)) +
    geom_density_ridges2(panel_scaling = FALSE, scale = 3) +
  scale_x_continuous(limits = c(0,7), breaks = seq(1,7,1)) +
  labs(title = "Agreeing on Definitions of People\n with Absolute and Relative Pitch",
       subtitle = paste("N = ", n_total_respondents),
       y = "Question",
       x = "   Strongly Disagree      Strongly Agree",
       fill = "Question Bank") +
  theme_bw() +
  viridis::scale_fill_viridis(discrete = TRUE, begin = .1, end = .8, alpha = .75)

people_plot

ggsave(filename = "img/fig/p2p_peopleplot.png", people_plot, dpi = 300, height = 9, width = 9)

  ```


## Column C

### Qualitative Breakdown Histogram

### Choice Quotes 

